---
title: "FRRO2Compare"
author:
- Douglas A. Campbell
- Maximilian Berthold
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
Compare [O2] to FRRf data.

Fit slopes to O2data over time windows defined by FRRf changes in PAR.
Trim O2 data nests to remove first 35 rows (~ 35 s) of 180 rows (~ 180 s) to avoid initial induction period.
Compare O2 slopes to FRR ETR estimates.


## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "FluorO2"
#Temporary RunDate during auditing
RunDate <- "20210609"
DataInO2 <- file.path("..","ImportData", "Optode")
DataInFRRf <- file.path("..","ImportData", "FRRf")
DataOut <- file.path("..", "FitData")
CatalogPath <- file.path("~/Dropbox/MURIS/MURIS_catalog.csv")

```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
#library(knitr)
#library(zoo)
# library(googlesheets4)
# library(googledrive)
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

Import MetaData catalog from MURIS
Improve this if we generalize the approach.
```{r}
MetaData <- read_csv(file = CatalogPath)
```


This chunk reads in a MetaData catalog from googlesheets 
```{r load Catalog, now as a google sheet}
# gs4_deauth()
# #deauthorizes access to googlesheet
# 
# MetaCatalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
# # sheet is read in by sheet ID, obtained from the URL of the sheet.
# # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
# # ggplot/dplyr doesn't like working with a dataframe of lists.
# # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# # To fix this, first drop all rows missing WL, then unlist.
# # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
# 

# as.data.frame(MetaCatalog)
```


Read in O2Data and FRRfData
Make this more general as we accumulate more files.
```{r read data}
#temporary hack to cope with run date; replace with GREP? or map?
O2Data <- readRDS(file = file.path(DataInO2, paste("FluorO2_",RunDate, "_O2Data.Rds", sep = "")))
FRRfData <- readRDS(file = file.path(DataInFRRf, paste("FluorO2_", RunDate, "_SolFitsTrim.Rds", sep = "")))

```

Remove missing rows, reconcile time formats
```{r remove missing rows}
O2Data <- O2Data %>%
  filter(!is.na(LR_s)) %>%
  mutate(Date = dmy(Date),
         AbsTime = as.period(AbsTime))

FRRfData <- FRRfData %>%
  filter(!is.na(LR_s))
```

```{r prelimplot}
O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  #geom_point(aes(x = FRRfData$LR_s, y = FRRfData$JVPSII_aLHIIminmax)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfData %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = JVPSII_aLHIIminmax)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfData %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = JVPSII_ETRqpOxbo)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfData %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = ETRqpOxbo)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfData %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = (ETRqpOxbo * Fomin/Sig_m2psii))) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()
```

## Try Simple left_join, in case times line up

```{r leftjoin}
O2SlopeData <- left_join(x = O2Data, y = FRRfData, by = c(c("Date" = "ObsDate"), c("AbsTime" = "ObsTime"), "CultureID", "Ex_WL"), suffix = c("O2", "FRRf"), keep = FALSE) %>%
  select(c("Date":"LR_sFRRf", "ActPAR_photonsm2s"))

```

```{r O2FRRfprelimplot}
O2SlopeData %>%
  #filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = LR_sO2, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_sO2, y = ActPAR), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

```

Interpolate ActPAR estimates across entire time axis
```{r interpolate FRRf estimates}
#http://publish.illinois.edu/spencer-guerrero/2014/12/11/2-dealing-with-missing-data-in-r-omit-approx-or-spline-part-1/
#https://dplyr.tidyverse.org/dev/articles/colwise.html
#Interpolation causes problems with final rows that repeat last value.

interpolate <- function(x){zoo::na.locf(x, na.rm = FALSE, fromLast = TRUE, type = "l", maxgap = Inf)}

O2SlopeData <- O2SlopeData %>%
  mutate(ActPARinter = interpolate(ActPAR),
         Dark1sinter = interpolate(Dark1s), 
         LR_sFRRfinter = interpolate(LR_sFRRf), .after = Temp_C)
         
         #ActPAR_photonsm2sinter = interpolate(ActPAR_photonsm2s),
         #JVPSIIinter = interpolate(JVPSII_aLHIIminmax)

# test <- O2SlopeData %>%
#   filter(CultureID == "MaBe3433",
#          #LR_sO2 < 450,
#         Ex_WL == "590")
# 
# test %>%
#    #filter(Dark1sinter == 0) %>%
#    ggplot() +
#   geom_point(aes(x = LR_sO2, y = O2_umolL, colour = Ex_WL)) +
#  geom_point(aes(x = LR_sO2, y = ActPARinter, colour = "black")) +
#     geom_point(aes(x = LR_sO2, y = Dark1sinter), colour = "red") +
#   scale_colour_manual(values = Colours_nm) +
#   facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
#   theme_bw()
```

Check whether ActPARinter worked properly
Need to check whether Dark1sinter worked properly
Need to filter for Dark1sinter == 0 before slope estimations or plotting vs. ActPARinter
```{r O2FRRfprelimplot2}
O2SlopeData %>%
  #filter(Dark1sinter == 0) %>%
  ggplot() +
  geom_point(aes(x = LR_sO2, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_sO2, y = ActPARinter), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

#filter CultureID with negative O2slope throughout and with aberrant ActPARinter
#recheck with Max about FRRf file processing to recuperate ActPARinter
O2SlopeData %>%
  #filter(Dark1sinter == 0) %>%
  #filter(CultureID != "MaBe3432") %>%
  #filter(CultureID != "MaBe3431") %>%
  #filter(CultureID != "MaBe3433" | Ex_WL != "590") %>%
  #filter(CultureID %in% c("MaBe3433", "MaBe3436")) %>%
  filter(CultureID != "MaBe3437",
         CultureID != "MaBe3438") |> 
  ggplot() +
  geom_point(aes(x = LR_sO2, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_sO2, y = ActPARinter), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

```

Estimate O2 slopes over LR PAR step ranges
Be careful with nesting!  Multiple steps at single ActPARinter
Filter out first 30 s of each ActPARinter set to skip 'induction' phase.
Filter out last 5 s to avoid Dark1s = 1 rows
```{r O2slopes}
induction_s = 35
end_s = 175

O2Slopes <- O2SlopeData %>%
  filter(Dark1sinter == 0) %>%
  #filter(CultureID != "MaBe3431") %>%
  #filter(CultureID != "MaBe3433" | Ex_WL != "590") %>%
  #filter(CultureID %in% c("MaBe3433", "MaBe3436")) %>%
  filter(CultureID != "MaBe3437",
         CultureID != "MaBe3438") %>%
  nest(O2data = -c(Date, CultureID, Ex_WL, filenameO2, ActPARinter, LR_sFRRfinter)) %>% 
  #nest(O2data = c(Date, AbsTime, LR_sO2, O2_umolL, Temp_C, ActPARinter, filenameO2)) %>%
  mutate(O2lm = map(O2data,  possibly(~ lm(O2_umolL[induction_s:end_s] ~ as.numeric(AbsTime[induction_s:end_s]), data = .x), otherwise = NULL)),
         O2lm_tidy = map(O2lm, possibly(tidy, otherwise = NULL))) %>%
  select(-c(O2data, O2lm)) %>%
  unnest(cols = O2lm_tidy) %>%
  filter(term  != "(Intercept)") %>%
  select(-term) %>%
  rename(O2_umolLs = estimate) %>%
  group_by(Date, filenameO2, CultureID, Ex_WL) %>% #careful with group_by; this only works with a single replication of each LR
  mutate(O2evln_O2ls = (O2_umolLs - min(O2_umolLs)) * 6.022e17) %>%
  ungroup()

#Decide how to handle subtraction of dark O2 slopes to estimate gross O2 evln
#mutate(O2evln_O2ls_ALT = (O2_umolLs - mean(O2_umolLs[1], O2_umolLs[5]))) %>%
 #- (mean(O2_umolLs[1],O2_umolLs[5])))*6.022e17
```

```{r O2slopeplots}

O2Slopes %>%
  ggplot() +
  geom_line(aes(x = ActPARinter, y = O2_umolLs, colour = Ex_WL)) +
    scale_colour_manual(values = Colours_nm) +
    facet_grid(cols = vars(CultureID), rows = vars(Ex_WL)) +
    theme_bw()

O2Slopes %>%
  ggplot() +
  geom_line(aes(x = ActPARinter, y = O2evln_O2ls, colour = Ex_WL)) +
    scale_colour_manual(values = Colours_nm) +
    facet_grid(cols = vars(CultureID), rows = vars(Ex_WL)) +
    theme_bw()
```

Merge O2Slopes Data with FRRf Data and Catalog

```{r}
O2FRRfMeta <- left_join(x = FRRfData, y = O2Slopes, by = c(c("ObsDate" = "Date"),  "CultureID", "Ex_WL", "ActPAR" = "ActPARinter"), suffix = c("FRRf", "O2"), keep = FALSE) %>%
  left_join(x = ., y = MetaData, by = c("CultureID" = "id"))
```


Cross plots of O2 evolution and FRRf electron transport
```{r O2FRRfcrossplots}
O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  theme_bw()

O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_ETRqpOxbo > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()
```

Fit regressions of FRRf estimators vs. O2evln
```{r FRRFO2regressions}
O2FRRfMetaNest <-  O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  nest(data = -c(Ex_WL)) %>%
  mutate(
  JVPSII_aLHIIminmax_O2 = map(data, possibly(~lm(JVPSII_aLHIIminmax ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_O2_predict = map(JVPSII_aLHIIminmax_O2, possibly(augment, otherwise = NULL)),
  JVPSII_O2_tidied =  map(JVPSII_aLHIIminmax_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_O2_param = map(JVPSII_aLHIIminmax_O2, possibly(glance, otherwise = NULL)),
  JVPSII_ETRqpOxbo_O2 = map(data, possibly(~lm(JVPSII_ETRqpOxbo ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_ETRqpOxbo_O2_predict = map(JVPSII_ETRqpOxbo_O2, possibly(augment, otherwise = NULL)),
  JVPSII_ETRqpOxbo_O2_tidied =  map(JVPSII_ETRqpOxbo_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_ETRqpOxbo_O2_param = map(JVPSII_ETRqpOxbo_O2, possibly(glance, otherwise = NULL))
  )



O2FRRfMetaNest %>%
  unnest(JVPSII_O2_predict) %>%
  ggplot() +
  geom_line(aes(x = O2evln_O2ls, y = .fitted), colour = "black", linetype = "dashed") +
 # geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
 #   geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax),colour = "darkgreen") +
  geom_point(aes(x = O2evln_O2ls, y = .resid), colour = "darkred", size = 0.1) +
  geom_hline(yintercept = 0,linetype = "dashed") +
  facet_grid(cols = vars(Ex_WL)) +
  theme_bw()

O2FRRfMetaNest %>%
  unnest(JVPSII_O2_tidied)

O2FRRfMetaNest %>%
  unnest(JVPSII_ETRqpOxbo_O2_predict) %>%
  ggplot() +
  geom_line(aes(x = O2evln_O2ls, y = .fitted), colour = "black", linetype = "dashed") +
 # geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
 #   geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo),colour = "darkgreen") +
  geom_point(aes(x = O2evln_O2ls, y = .resid), colour = "darkred", size = 0.1) +
  geom_hline(yintercept = 0,linetype = "dashed") +
  facet_grid(cols = vars(Ex_WL)) +
  theme_bw()

O2FRRfMetaNest %>%
  unnest(JVPSII_ETRqpOxbo_O2_tidied)

```


```{r save O2FRRfMeta}
saveRDS(O2FRRfMeta, file.path(DataOut, paste(Project, RunDate, "O2FRRfMeta.Rds", sep = "_"), fsep = .Platform$file.sep))
```


