---
title: "FRRO2Pooled"
author:
- Douglas A. Campbell
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# To Do
Run workflow with Mireille & Sylwia data

# Done

Do comparison of achieved PAR within the cuvette +/- TC.
Do Mireille or Sylwia have this data.

Does water differentially attenuate blue light?

# Introduction
Pool [O2] vs. FRRf data from multiple runs.

i. Compare O2 l~-1~ s~-1~ slopes for each PAR to estimates of PSII ETR e- PSII~-1~ s~-1~ taken from FRR measures at that same PAR level.
  This calibration can gives us an estimate of [PSII] because:
  O2 l~-1~ s~-1~ = (e- PSII~-1~ s~-1~)/4 * [PSII], so
  [PSII] = O2 l~-1~ s~-1~ * 4/(e- PSII~-1~ s~-1~)

For a given sample [PSII] should be a constant; any change in O2 l~-1~ s~-1~ with increasing PAR or different Ex_WL should be driven solely by changes in e- PSII~-1~ s~-1~.
If apparent [PSII] for a given sample changes this indicates issues with measurements, as for example recycling of electrons leaving PSII back to reduction of O2 induced under high light, which lowers measured O2 l~-1~ s~-1~.

Other influences could include different levels of fluorescence from sources outside PSII generating differential distortions on the fluorescence based estimator of e- PSII~-1~ s~-1~.

[PSII] is intrinsically interesting as a core element of photophysiology and cellular composition.  It also provides a reality check on other fluorescence based metrics.

ii. Sort [PSII] by sample and compare to [Chl] for the same sample to test for consistency and detect systematic variations which could be used to filter downstream data.

In principle we can then use [PSII] from a sample to calibrate a fluorescence estimator such as Fo/sigmaPSII from the same sample, which might be specific to a particular Ex_WL, or generalized.

We can then generate JVPSII through:
PSII ETR X {(Fo/sigmaPSII) ~ [PSII] x calibration}

Calibration may be gain specific for fluorometer depending upon whether reported F levels are compensated for gain.
Chelsea fluorometers auto-compensate for gain to give 'consistent' Fo readings, but I am not sure about the Solisense.

iii. Compare O2 l~-1~ s~-1~  slopes for each PAR to direct  estimates of JVPSII e- L~-1~ s~-1~ taken directly from FRR measures using the aLHII approach.

aLHII is the total effective absorbance cross section serving the pool of PSII in a volume of sample.

{aLHII = sigmaPSII x [PSII] x calibration}

  This direct calibration gives us a calibratable, fluorescence based estimate of e- L~-1~ s~-1~, for later comparison with growth rates, cell counts, etc.

Import [Chl] data for screening results and generating [PSII]:[Chl].

iv) Cross compare TC and noTC and report results to SCOR working group 156

Add bibliography
Add citations

## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```


```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
#library(knitr)
#library(zoo)
library(googlesheets4)
library(googledrive)
```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "FluorO2"
#Temporary RunDate during auditing
DataIn<- file.path("..","FitData")
DataOut <- file.path("..", "ProcessData")
#CatalogPath <- file.path("~/Dropbox/MURIS/MURIS_catalog.csv")
ChloroGoogle <- "https://docs.google.com/spreadsheets/d/1yhmuv7V0clcLpqlsTYBMtfIcsS8Rp5yjtkRH2ktZwk0/edit#gid=0"


#Chlorophyll RFU calibration
#https://www.dropbox.com/sh/afag5s8oc5d7hpf/AABK56di0J5-5vVoFuIdvDJOa?dl=0

#Does chl calibration refer to the extract or to the original sample with a fixed dilution of sample into extract?
#Analytical Standard Used: Supelco Chlorophyll a Analytical Standard, ordered from Sigma (#96145-1MG). Standard Preparation: Standard was redissolved in 90% acetone to prepare a secondary standard of ~5000 µg Chl a liter-1. This secondary standard is stored at -20C and is used to prepare a five-point linear calibration curve.

# Calibration Equation: (Value in RFU - [B]) / [M] = Value in µg Chl a / liter extraction solvent, where B is the intercept and M is the slope of the linear regression of the Chl a standard response.
# We need to re-run the Turner Calibration and post XY data to GoogleSheet to re-validate these values
RFUIntercept_ugL = 0.7656
RFUSlope_ugL = 7.064
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

#Colour blind friendly palette
# blindcolours = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

```

## Read Chlorophyll Data
Dynamically generate Chlorophyll Calibration from GoogleSheet with Turner Calibration Values
```{r read chlorophyll data}
gs4_deauth()
ChloroData <- read_sheet(ChloroGoogle)

#convert DATE, TIME
ChloroData <- ChloroData %>%
  mutate(DATE = ymd(DATE))

#volume correction for RFU
#fine calibration table?

#convert to Chla_ugL
#Does chl calibration refer to the extract or to the original sample with a fixed dilution of sample into extract?

#RFUIntercept_ugL = 0.7656
#RFUSlope_ugL = 7.064

ChloroData <- ChloroData %>%
   mutate(Chl_dil = (Reading_rfu - RFUIntercept_ugL)/RFUSlope_ugL,
          Chl_ugL = Chl_dil * ((SolventVol_ul + SampleVol_ul)/SampleVol_ul))

#collapse Replicates
ChloroDataAver <- ChloroData %>%
  group_by(CultureID, DATE) %>%
  summarize (Chl_ugL_mean = mean(Chl_ugL, na.rm = TRUE), .groups = "keep") %>%
  ungroup()

```

## List O2FRRfData
```{r}
O2FRRfFiles <- list.files(path = DataIn, full.names = TRUE) %>%
  str_subset(pattern = "Nest", negate = TRUE)

O2FRRfFiles
```

Read in .Rmd manually and check for missing columns
```{r}
# All.list <- list(FluorO2_20211210_noTC_O2FRRfMeta, FluorO2_20211210_TC_O2FRRfMeta, FluorO2_20211213_noTC_O2FRRfMeta, FluorO2_20211213_TC_O2FRRfMeta)
#  my_function <- function(data_frame){
#      require(dplyr)
#      x <- tibble(`var_name` = colnames(data_frame),
#                  `var_type` = sapply(data_frame, class))
#      return(x)
#  }
# 
# 
#  target <- lapply(1:length(All.list),function(i)my_function(All.list[[i]]) %>%
#                       mutate(element =i)) %>%
#      bind_rows() %>%
#      spread(element, var_type)
```


## Read O2FRRfData
Many blank rows; consider re-working FRRO2Compare.Rmd
MetaData from MURIS previously merged with O2FRRf files.

```{r read O2FRRfData}
#issue with Character vs. Numeric for files 7-9 with column PQP_Size, source and mc 

read_plus_rds = function(Flnm) {readRDS(Flnm) %>%
    mutate(Filename = Flnm) %>%
    select(-c(PQP_Size, source, mc))
  }


O2FRRfAll <- O2FRRfFiles %>%
  map_df(~read_plus_rds(Flnm = .)) %>%
  filter(!is.na(filenameO2)) %>%
  select(
    where(
      ~!all(is.na(.x)) #remove irrelevant columns
    )
  )

```


```{r leftjoin ChloroDataAver to O2FRRfData}
O2FRRfPool <- left_join(x = O2FRRfAll, y = ChloroDataAver, by = c("CultureID", c("ObsDate" = "DATE")), suffix = c("O2FRRf", "Chl"), keep = FALSE)

colnames(O2FRRfPool)
```


```{r prelimplot}
O2FRRfPool %>%
  filter(Ex_WL == 445) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = O2evln_O2ls, colour = as.factor(TempContO2))) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(ObsDate), cols = vars(CultureID)) +
  theme_bw()


O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = ETRqpOxbo, colour = as.factor(TempContO2))) +
  geom_smooth(aes(x = ActPARCorr, y = ETRqpOxbo, colour = as.factor(TempContO2)), method = "lm") +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

O2FRRfPool %>%
  filter(Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = ETRCtauav, y = ETRGorbo, colour = as.factor(TempContO2))) +
  geom_smooth(aes(x = ETRCtauav, y = ETRGorbo, colour = as.factor(TempContO2)), method = "lm") +
  #scale_colour_manual(values = Colours_nm) +
  #facet_grid(rows = vars(Ex_WL)) +
  coord_fixed(ratio = 1) +
  theme_bw()

O2FRRfPool %>%
  filter(#Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRtauav_FoSig, colour = as.factor(Ex_WL))) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRtauav_FoSig, colour = as.factor(Ex_WL)), method = "lm") +
  #scale_colour_manual(values = Colours_nm) +
  #facet_grid(rows = vars(Ex_WL)) +
  #coord_fixed(ratio = 1) +
  theme_bw()

O2FRRfPool %>%
  filter(#Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRtauav_aLHII_Sig, colour = as.factor(Ex_WL))) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRtauav_aLHII_Sig, colour = as.factor(Ex_WL)), method = "lm") +
  #scale_colour_manual(values = Colours_nm) +
  #facet_grid(rows = vars(Ex_WL)) +
  coord_fixed(ratio = 1) +
  theme_bw()

O2FRRfPool %>%
  filter(#Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = ETRqp, y = ETRCtauav, colour = as.factor(Ex_WL))) +
  geom_smooth(aes(x = ETRqp, y = ETRCtauav, colour = as.factor(Ex_WL)), method = "lm") +
  #scale_colour_manual(values = Colours_nm) +
  #facet_grid(rows = vars(Ex_WL)) +
  coord_fixed(ratio = 1) +
  theme_bw()

O2FRRfPool %>%
  filter(#Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = ETRqpOxbo, y = ETRqp, colour = as.factor(Ex_WL))) +
  geom_smooth(aes(x = ETRqpOxbo, y = ETRqp, colour = as.factor(Ex_WL)), method = "lm") +
  #scale_colour_manual(values = Colours_nm) +
  #facet_grid(rows = vars(Ex_WL)) +
  coord_fixed(ratio = 1) +
  theme_bw()

# ggplot() +
#   #geom_point(aes(x = ActPARCorr, y = O2evln_O2ls, colour = Ex_WL)) +
#   geom_point(aes(x = O2FRRfPool %>% filter(Dark1s == 0) %>% filter(TempContO2 == "noTC") %>% pull(JVPSII_aLHIIminmax), y =  O2FRRfPool %>% filter(Dark1s == 0) %>% filter(TempContO2 == "TC") %>% pull(JVPSII_aLHIIminmax))) +
#   #scale_colour_manual(values = Colours_nm) +
#   #facet_grid(cols = vars(CultureID)) +
#   theme_bw()


```

Data exploration suggests:

JVPSII_aLHII shows good patterns of linear increase with light, but is not absolutely calibrated and is not normalized to biomass ([Chl]).

Linear increase with light is consistent with published cyanobacterial photophysiology that raw generation of e- at PSII increases steadily up to high light levels.

Saturating patterns of rising O2 elvn with increasing light are consistent with e- leaving PSII, emitting 'gross O2', which is then nearly immediately taken back up through e- flow back to O2; 'pseudocyclic' e- flow.

Discrepancy b/t JVPSII and O2 tells us about e- physiology across light levels (or among taxa x conditions).

These discrepancies can also be analyzed comparing PSII ETR e- PSII-1 s-1 with O2 L-2 s-1.

For calibration of JVPSII using O2 data, consider trimming to avoid light saturation region, particularly top light level with NoTC.

O2evln_O2ls was calculated by subtracting average slope of start and end respiration rates, but there may still be arithmetic or grouping issues b/c at 0 PAR O2evln_O2ls is not always zero and some data sets show a large displacement from 0.
Offsets particularly evident in runs with NoTC; runs with TC generally start ~0 indicating that initial and final respiration rates are similar.
Large upward offsets from O in NoTC runs suggest acceleration of respiration during the run.

Starting to wonder if calibrations should be run primarily (exclusively?) with TC.

But, JVPSII is similar b/t TC and NoTC so calibration using TC should be transferrable to NoTC.

Separate calibrations needed for x = O2evln_O2ls, y = JVPSII_aLHIIminmax for separate Ex_WL, indicating that Ex_WL differentially influences JVPSII_aLHIIminmax beyond the simple argument that PUR is higher for 590 nm than for 445 nm at a given PAR.

x = JVPSII_aLHIIdark, y = JVPSII_aLHIIminmax shows that JVPSII_aLHIIdark is systematically higher than JVPSII_aLHIIminmax, even though they are tightly correlated.
Different JVPSII need to be calibrated separately with O2 estimates.

PSII opening metrics (qp etc.) indicate that tau based estimators of 'C' may degrade under high PUR, which, coincidentally, only occurs under Ex_WL = 590 nm.
Alternately, tau based estimators may fail under 590 nm, but this seems less plausible b/c tau based estimates are taken from shape of a decay curve, and should not be influenced by fluorescence from outside PSII excited by 590 nm.

For some downstream estimators we need to pick an estimator of 'C' (Fraction of PSII closed).
All work for Ex_WL == 445 nm

#Cross plots to compare different PSII ETR estimators

Doug: Checked on arithmetic for JVPSII estimators; seem correct except possibly FoOxbo based upon Fomin instead of Fodark.
```{r ExWL blue JVPSII comparisons}

O2FRRfPool %>%
  filter(
         Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax, colour = as.factor(TempContO2))) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax, colour = as.factor(TempContO2)), method = "lm") +
  #facet_grid(rows = vars(Ex_WL)) +
  theme_bw()

O2FRRfPool %>%
  filter(
         Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIdark, colour = as.factor(TempContO2))) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_aLHIIdark, colour = as.factor(TempContO2)), method = "lm") +
  #facet_grid(rows = vars(Ex_WL)) +
  theme_bw()

O2FRRfPool %>%
  filter(
         Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRtau1, colour = as.factor(TempContO2))) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRtau1, colour = as.factor(TempContO2)), method = "lm") +
  #facet_grid(rows = vars(Ex_WL)) +
  theme_bw()

O2FRRfPool %>%
  filter(
         Ex_WL == 445,
         ActPARCorr != 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo, colour = as.factor(TempContO2))) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo, colour = as.factor(TempContO2)), method = "lm") +
  #facet_grid(rows = vars(Ex_WL)) +
  theme_bw()

```

# Facet ETRqp vs O2evln_O2ls by culture because different cultures have different [PSII]
```{r ExWL blue PSII ETR comparisons by culture}

O2FRRfPool %>%
  filter(
         ActPARCorr != 0,
         #Ex_WL == 445,
         #TempContO2 == "noTC"
         ) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls * 4, x = ETRqp, colour = as.factor(Ex_WL))) +
  geom_smooth(aes(y = O2evln_O2ls  * 4, x = ETRqp), method = "lm") +
  facet_grid(rows = vars(ObsDate), cols = vars(CultureID)) +
  theme_bw()

O2FRRfPool %>%
  filter(
         ActPARCorr != 0,
         #Ex_WL == 445,
         #TempContO2 == "noTC"
         ) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls  * 4, x = ETRCtau1, colour = as.factor(Ex_WL))) +
  geom_smooth(aes(y = O2evln_O2ls  * 4, x = ETRCtau1), method = "lm") +
  facet_grid(rows = vars(ObsDate), cols = vars(CultureID)) +
  theme_bw()

O2FRRfPool %>%
  filter(
         ActPARCorr != 0,
         #Ex_WL == 445,
         #TempContO2 == "TC"
         ) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls  * 4, x = ETRqp, colour = Ex_WL)) +
  geom_smooth(aes(y = O2evln_O2ls  * 4, x = ETRqp), method = "lm") +
  facet_grid(rows = vars(ObsDate), cols = vars(CultureID)) +
  theme_bw()


O2FRRfPool %>%
  filter(
         ActPARCorr != 0,
         #Ex_WL == 445,
         TempContO2 == "TC") %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls  * 4, x = ETRqp, colour = Ex_WL)) +
  geom_smooth(aes(y = O2evln_O2ls  * 4, x = ETRqp), method = "lm") +
  facet_grid(rows = vars(ObsDate), cols = vars(CultureID)) +
  theme_bw()

```

#Extract [PSII] by fitting models of O2evln_O2ls vs. ETRqp
445 nm and 590 nm data OK in principle for TC runs. In theory [PSII] does not change with excitation wavelength.
Less scatter with 445 nm.

Filter out MaBe3729 for 2021-12-10
Decided to filter out PCC6803 for now; seems to have a different relation b/t O2 & ETRqp
```{r}
ChlMW_gmol <- 893
umol_particles <- 6.022E17

PSII <- O2FRRfPool %>%
  filter(
         ActPARCorr != 0,
         TempContO2 == "TC") %>% 
  unite(IDCol, ObsDate, CultureID, remove = FALSE) %>%
  #filter(IDCol != "2021-12-10MaBe3729") %>%
#was unable to get filter(ObsDate != "2021-12-10" & CultureID != "MaBe3729")
# to work even though filter(ObsDate == "2021-12-10" & CultureID == "MaBe3729")
#gave the mirror image result

#force linear models through 0 b/c we are excluding data where O2evln_O2ls <= 0 and at 0 PAR PSIIETR has to equal 0.
  filter(strain != "PCC6803") %>%
  nest(O2ETRdata = -c(ObsDate, CultureID, strain, Chl_ugL_mean)) %>% 
  mutate(O2ETRlm = map(O2ETRdata,  possibly(~ lm(O2evln_O2ls ~ 0 + ETRqp, data = .x), otherwise = NULL)),
         O2ETRlm_tidy = map(O2ETRlm, possibly(tidy, otherwise = NULL))) %>%
  select(-c(O2ETRdata, O2ETRlm)) %>%
  unnest(cols = O2ETRlm_tidy) %>%
  filter(term  != "(Intercept)") %>%
  select(-term) %>%
  mutate(PSII_L = estimate * 4, #check if divided by 4 is the right thing to do
         PSII_L_se = std.error * 4) %>%
  mutate(Chl_L = Chl_ugL_mean /ChlMW_gmol * umol_particles,
         Chl_PSII =  Chl_L/PSII_L) #chl to molar

PSIIex445 <- O2FRRfPool %>%
  filter(
         ActPARCorr != 0,
         TempContO2 == "TC",
         Ex_WL == 445) %>% 
         #filter(ObsDate != "2021-12-10" & CultureID != "MaBe3729") %>%
  unite(IDCol, ObsDate, CultureID, remove = FALSE) %>%
  #filter(IDCol != "2021-12-10MaBe3729") %>%
  filter(strain != "PCC6803") %>%
  nest(O2ETRdata = -c(ObsDate, CultureID,  strain, Chl_ugL_mean, Ex_WL)) %>% 
  mutate(O2ETRlm = map(O2ETRdata,  possibly(~ lm(O2evln_O2ls ~ 0 + ETRqp, data = .x), otherwise = NULL)),
         O2ETRlm_tidy = map(O2ETRlm, possibly(tidy, otherwise = NULL))) %>%
  select(-c(O2ETRdata, O2ETRlm)) %>%
  unnest(cols = O2ETRlm_tidy) %>%
  filter(term  != "(Intercept)") %>%
  select(-term) %>%
  mutate(PSII_L = estimate * 4, #check if divided by 4 is the right thing to do
         PSII_L_se = std.error * 4) %>%
  mutate(Chl_L = Chl_ugL_mean /ChlMW_gmol * umol_particles,
         Chl_PSII = Chl_L/PSII_L) #chl to molar


PSIIex590 <- O2FRRfPool %>%
  filter(
         ActPARCorr != 0,
         TempContO2 == "TC",
         Ex_WL == 590) %>% 
         #filter(ObsDate != "2021-12-10" & CultureID != "MaBe3729") %>%
  unite(IDCol, ObsDate, CultureID, remove = FALSE) %>%
  #filter(IDCol != "2021-12-10MaBe3729") %>%
  filter(strain != "PCC6803") %>%
  nest(O2ETRdata = -c(ObsDate, CultureID,  strain, Chl_ugL_mean, Ex_WL)) %>% 
  mutate(O2ETRlm = map(O2ETRdata,  possibly(~ lm(O2evln_O2ls ~ 0 +ETRqp, data = .x), otherwise = NULL)),
         O2ETRlm_tidy = map(O2ETRlm, possibly(tidy, otherwise = NULL))) %>%
  select(-c(O2ETRdata, O2ETRlm)) %>%
  unnest(cols = O2ETRlm_tidy) %>%
  filter(term  != "(Intercept)") %>%
  select(-term) %>%
  mutate(PSII_L = estimate * 4, #check if divided by 4 is the right thing to do
         PSII_L_se = std.error * 4) %>%
  mutate(Chl_L = Chl_ugL_mean /ChlMW_gmol * umol_particles,
         Chl_PSII =  Chl_L/PSII_L) #chl to molar

PSII
PSIIex445
PSIIex590

#cross plots
ggplot() +
  geom_point(aes(x = PSIIex445$PSII_L, y = PSIIex590$PSII_L, colour = PSIIex445$strain)) +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  theme_bw()

ggplot() +
  geom_point(aes(y = PSIIex445$PSII_L, x = PSII$PSII_L, colour = PSIIex445$strain)) +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  theme_bw()
```

Some chlorophyll : PSII values seem to be off. 

Either Algebra is off, or [Chl] is too high, or [PSII] is underestimated.
Based upon reasonable range for [Chl], likely that [PSII] is sometimes underestimated?

Filtered out problematic PCC6803 values; possible issue with light attenuation?
Use PSIIex445 for now.

```{r PSII vs. Chl}

PSII %>%
  filter(PSII_L > 0) %>% 
  ggplot() +
  geom_point(aes(y = Chl_L, x = PSII_L)) +
  geom_smooth(aes(y = Chl_L, x = PSII_L), method = "lm") +  
  theme_bw()

PSIIex445 %>%
  filter(PSII_L > 0) %>% 
  ggplot() +
  geom_point(aes(y = Chl_L, x = PSII_L, colour = CultureID)) +
  geom_smooth(aes(y = Chl_L, x = PSII_L), method = "lm") +  
  theme_bw()

PSIIex590 %>%
  filter(PSII_L > 0) %>% 
  ggplot() +
  geom_point(aes(y = Chl_L, x = PSII_L, colour = CultureID)) +
  geom_smooth(aes(y = Chl_L, x = PSII_L), method = "lm") +  
  theme_bw()
```

For PSIIex445
7.5e17 Chl l-1 / 6 e14 PSII_L ~ 1250 Chl : PSII
It should be in the range of 250 to 1500.

Bottom up guesstimate:
1 PSII : 2 PSI
1 x (36 PSII chl) : 2 x (96 PSI chl)
36 PSII chl + 192 PSI chl = 228 chl per PSII.

1 x (36 PSII chl) : 3 x (96 PSI chl)
324 chl per PSII,

11250 chl per PSII implies

11250 = (1 * 36 PSII chl) + (x * 96 PSI chl)
(1250 - 36)/96
Implies ~13 PSI : PSII
This is at the upper end of plausibility for a cyanobacteria, and suggests an under-estimation of PSII content in our system.


Another cross check:
7.5e17 chl L-1 is 1.25 umol Chl L-1
1.25 umol chl L-1 x 893 ug chl/umol chl = 1122 ug chl L-1 = 1.2 ug chl ml-1 which is  plausible for cultures which contain PBSomes, but probably a bit dark.

#Calibrate Fo/SigmaPSII using [PSII] from Ex_WL = 445 nm
```{r}
O2FRRfPoolPSII <- left_join(x = O2FRRfPool %>% filter(Ex_WL == 445), y = PSIIex445, by = c("CultureID", "ObsDate"))

O2FRRfPoolPSII %>% ggplot() +
  geom_point(aes(x = Fomin/Sigmax, y = PSII_L, colour = CultureID)) + 
  geom_smooth(aes(x = Fomin/Sigmax, y = PSII_L), method = "lm") +
  theme_bw()

O2FRRfPoolPSII %>% ggplot() +
  geom_point(aes(x = Fodark/Sigdark, y = PSII_L, colour = CultureID)) + 
  geom_smooth(aes(x = Fodark/Sigdark, y = PSII_L), method = "lm") +
  theme_bw()
```

High scatter in attempt to calibrate Fomin/Sigmax with [PSII].
May need additional runs?

# Calibration of JVPSII with umol O2 L-1 s-1 * 4
Note filters to restrict data set.
```{r O2FRRfChlprelimplot}
O2FRRfPool %>%
  filter(
         TempContO2 == "TC",
         ActPARCorr != 0,
         Ex_WL == 445,
         O2evln_O2ls > 0,
         strain != "PCC6803") %>%
  ggplot() +
  geom_point(aes(x = JVPSII_aLHIIminmax, y = O2evln_O2ls * 4, size = Chl_ugL_mean, colour = strain)) +
  geom_smooth(aes(x = JVPSII_aLHIIminmax, y = O2evln_O2ls * 4, size = Chl_ugL_mean), method = "lm") +
 facet_grid(rows = vars(Ex_WL), cols = vars(strain)) +
  theme_bw()

O2FRRfPool %>%
  filter(
         TempContO2 == "TC",
         ActPARCorr != 0,
         Ex_WL == 445,
         O2evln_O2ls > 0,
         strain != "PCC6803") %>%
  ggplot() +
  geom_point(aes(x = JVPSII_aLHIIminmax, y = O2evln_O2ls * 4, size = Chl_ugL_mean, colour = strain)) +
  geom_smooth(aes(x = JVPSII_aLHIIminmax, y = O2evln_O2ls * 4, size = Chl_ugL_mean), method = "lm") +
 facet_grid(rows = vars(Ex_WL)) +
  theme_bw()

```

```{r lm PSIIETR_O2}
#significant effect of strain
#significant effect of Ex_WL
#note filters to restrict dataset

#force lm through 0 b/c at 0 PAR JVPSII = 0 and we are excluding data from PAR = 0
# tidy(O2FRRfPool %>% 
#   filter(
#          TempContO2 == "TC",
#          ActPARCorr != 0,
#          Ex_WL == 445,
#          O2evln_O2ls > 0) %>%
#   filter(JVPSII_aLHIIminmax > 0) %>%
#   lm(O2evln_O2ls * 4 ~ 0 + JVPSII_aLHIIminmax + strain, data = .))

# tidy(O2FRRfPool %>% 
#   filter(
#          TempContO2 == "TC",
#          ActPARCorr != 0,
#          Ex_WL == 445,
#          O2evln_O2ls > 0) %>%
#   filter(JVPSII_aLHIIminmax > 0) %>%
#   lm(O2evln_O2ls  * 4 ~ JVPSII_aLHIIminmax + Ex_WL + strain, data = .))

# O2FRRfStrainNest <- O2FRRfPool %>%
#   filter(
#          TempContO2 == "TC",
#          ActPARCorr != 0,
#          Ex_WL == 445,
#          O2evln_O2ls > 0) %>%
#   filter(JVPSII_aLHIIminmax > 0) %>%
#   nest(O2FRRf = -c(strain, Ex_WL)) %>%
#   mutate(PSIIETRO2lm = map(O2FRRf, possibly(~ lm(O2evln_O2ls * 4 ~ 0 +  JVPSII_aLHIIminmax, data = .x), otherwise = NULL)),
#          PSIIETRO2lm_tidy = map(PSIIETRO2lm, possibly(tidy, otherwise = NULL)))


O2FRRf445_Nest <- O2FRRfPool %>%
  filter(
         TempContO2 == "TC",
         ActPARCorr != 0,
         Ex_WL == 445,
         O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  nest(O2FRRfdata = -c(Ex_WL)) %>%
  mutate(PSIIETRO2lm = map(O2FRRfdata, possibly(~ lm(O2evln_O2ls * 4 ~ 0 +  JVPSII_aLHIIminmax, data = .x), otherwise = NULL)),
         PSIIETRO2lm_tidy = map(PSIIETRO2lm, possibly(tidy, otherwise = NULL)))

O2FRRf445lm <- O2FRRf445_Nest %>% 
  unnest(PSIIETRO2lm_tidy)

O2FRRf445_No6803Nest <- O2FRRfPool %>%
  filter(
         TempContO2 == "TC",
         ActPARCorr != 0,
         Ex_WL == 445,
         O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  filter(strain != "PCC6803") %>%
  nest(O2FRRfdata = -c(Ex_WL)) %>%
  mutate(PSIIETRO2lm = map(O2FRRfdata, possibly(~ lm(O2evln_O2ls * 4 ~ 0 +  JVPSII_aLHIIminmax, data = .x), otherwise = NULL)),
         PSIIETRO2lm_tidy = map(PSIIETRO2lm, possibly(tidy, otherwise = NULL)))

O2FRRf445_No6803lm <- O2FRRf445_No6803Nest %>% 
  unnest(PSIIETRO2lm_tidy)

#O2FRRf445_lms <- rbind(O2FRRf445lm, O2FRRf445_No6803lm
                       
bindAndSource <-  function(df1, df2) { 
  df1$source <- as.character(match.call())[[2]]
  df2$source <- as.character(match.call())[[3]]
  rbind(df1, df2)
} 

O2FRRf_lms <- bindAndSource(O2FRRf445_Nest %>% 
  unnest(PSIIETRO2lm_tidy), O2FRRf445_No6803Nest %>% 
  unnest(PSIIETRO2lm_tidy))

#alternative to 'nest' by Strain & Ex_WL to generate single nested dataframe
# PSIIETR_O2_lm_445 <- tidy(O2FRRfPool %>%
#   filter(
#          TempContO2 == "TC",
#          ActPARCorr != 0,
#          Ex_WL == 445,
#          O2evln_O2ls > 0) %>%
#   filter(JVPSII_aLHIIminmax > 0) %>%
#   filter(Ex_WL == "445") %>%
#   lm(O2evln_O2ls * 4 ~ 0 + JVPSII_aLHIIminmax, data = .))

# PSIIETR_O2_lm_445
# 
# PSIIETR_O2_lm_590 <- tidy(O2FRRfPool %>%
#   filter(
#          TempContO2 == "TC",
#          ActPARCorr != 0,
#          Ex_WL == 590,
#          O2evln_O2ls > 0) %>%
#   filter(JVPSII_aLHIIminmax > 0) %>%
#   lm(O2evln_O2ls * 4 ~ 0 +  JVPSII_aLHIIminmax, data = .))
# 
# PSIIETR_O2_lm_590
```

```{r PSIIETR_O2_lm_plot}
#{} around ggplot call allow us to use .$ to set Title etc. to values from filtered dataframe
#note '.' in ggplot(.)

O2FRRfPool_plot <- O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  filter(Ex_WL == 445) %>%
         {
  ggplot(.) +
  geom_point(aes(x = JVPSII_aLHIIminmax, y = O2evln_O2ls * 4, size = Chl_ugL_mean, colour = strain)) +
  geom_abline(intercept = 0, slope = O2FRRf_lms$estimate[1]) +
  geom_abline(intercept = 0, slope = O2FRRf_lms$estimate[1] + O2FRRf_lms$std.error[1], linetype = "dotted") +
  geom_abline(intercept = 0, slope = O2FRRf_lms$estimate[1] - O2FRRf_lms$std.error[1], linetype = "dotted") +
  geom_abline(intercept = 0, slope = O2FRRf_lms$estimate[2], linetype = "dashed") +
  geom_abline(intercept = 0, slope = O2FRRf_lms$estimate[2] + O2FRRf_lms$std.error[12], linetype = "dotted") +
  geom_abline(intercept = 0, slope = O2FRRf_lms$estimate[2] - O2FRRf_lms$std.error[2], linetype = "dotted") +
  labs(title =  paste("Ex_WL ", unique(.$Ex_WL), "nm"), subtitle = "Solid Regression all strains; Dashed excludes PCC6803") +
  theme_bw()}


 O2FRRfPool_plot
```



```{r save O2FRRfMeta}

ggsave(filename = file.path(DataOut, "O2FRRfPool_plot.png"), plot = O2FRRfPool_plot)

saveRDS(O2FRRf_lms, file.path(DataOut, paste(Project, "O2FRRf_lms.Rds", sep = "_"), fsep = .Platform$file.sep))
```


