---
title: "FRRO2Compare"
author:
- Douglas A. Campbell
- Maximilian Berthold
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
Compare [O2] to FRRf data.

Define time windows defined by changes in PAR imposed by script from FRRf changes in PAR.
For each run create a series of nests of [O2] data from optode for each PAR level and each TempCont setting.
Trim [O2] data nests to remove first 35 rows (~ 35 s) of 180 rows (~ 180 s) to avoid initial induction period.
Fit slopes of umol O2  l~-1~ s~-1~ for each PAR level nest.
Generate estimates of gross umol O2  l~-1~ s~-1~ by subtracting dark respiration rates.
  Initial and final O2 respiration rate estimators; average? chose?
  
Plot gross umol O2  l~-1~ s~-1~ vs. PAR to detect outliers.

i. Compare O2 l~-1~ s~-1~ slopes for each PAR to estimates of PSII ETR e- PSII~-1~ s~-1~ taken from FRR measures at that same PAR level.
  This calibration gives us an estimate of [PSII] because:
  O2 l~-1~ s~-1~ = (e- PSII~-1~ s~-1~)/4 * [PSII], so
  [PSII] = O2 l~-1~ s~-1~ * 4/(e- PSII~-1~ s~-1~)

For a given sample [PSII] should be a constant; any change in O2 l~-1~ s~-1~ with increasing PAR or changing actinic light colour should be driven solely by changes in e- PSII~-1~ s~-1~.  If apparent [PSII] changes this indicates issues with measurements, as for example recycling of electrons leaving PSII back to reduction of O2 induced under high light, which lowers measured O2 l~-1~ s~-1~, or distortions under different excitation colours 450 nm vs. 590 nm.

ii.  Comparing results from different samples and light levels and light qualities, generate calibration(s) for fluorescence based estimators of [PSII] like Fo/sigmaPSII.
  
iii. Compare O2 l~-1~ s~-1~  slopes for each PAR to estimates of JVPSII e- L~-1~ s~-1~ taken from FRR measures.
  This direct calibration gives us a fluorescence based calibrated estimate of e- L~-1~ s~-1~, for later comparison with growth rates, cell counts, etc.

# Set General Variable Values
## Run specific variables start at Line 122

## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set general project variables}
#"..", takes up a level in the directory path
Project <- "FluorO2"

DataInO2 <- file.path("..","ImportData", "Optode")
DataInFRRf <- file.path("..","ImportData", "FRRf")
DataOut <- file.path("..", "FitData")
CatalogPath <- file.path("../MURIS/MURIS_catalog.csv")

```

```{r set constants}
photons_umol = 6.022E17
A2_m2 = 1E20
us_s = 1000000
```


```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
#library(knitr)
#library(zoo)
library(googlesheets4)
library(googledrive)
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

Import MetaData catalog from MURIS
Improve this if we generalize the approach.
```{r}
# MetaData <- read_csv("../../MURIS_catalog.csv") #two levels from R-folder
```


This chunk reads in a MetaData catalog from googlesheets 
```{r load Catalog, now as a google sheet}
gs4_deauth()

MetaData <- 
read_sheet("https://docs.google.com/spreadsheets/d/1wik41fMOiiA1gxLGtU8y3zpkrY1rqdMqXqQZs__sf-E/edit?usp=sharing")

#%>%
# sheet is read in by sheet ID, obtained from the URL of the sheet.
# read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
# ggplot/dplyr doesn't like working with a dataframe of lists.
 # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# # # To fix this, first drop all rows missing WL, then unlist.
# # # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
# # 
# 
# # as.data.frame(MetaCatalog)
```


```{r read FRRf data across all runs}
#Temporary RunDate during auditing
RunDateFRRf <- "Refit"
FRRfData <- readRDS(file = file.path(DataInFRRf, paste("FluorO2_", RunDateFRRf, "_SolFitsTrim.Rds", sep = "")))

```

# Set Run Specific Variables for each set of O2 Data; TC/noTC, RunDateOxy, StrainID

```{r set run specific O2 variables}
  #FRRf refit includes data from both dates
RunDateOxy <- 20211210
  #20211213 alternate date
Cuvette <- "TC"
StrainID <- "MaBe3729"

```

#ReFit FRRf data includes multiple run dates; filter to match selected O2 data
```{r filter FRRfData}
FRRfDataLight <- FRRfData %>%
  filter(!is.na(LR_s)) %>%
  filter(TempCont == Cuvette) %>%
  filter(CultureID == StrainID) %>%
  filter(Dark1s == 0) %>%
  filter(ObsDate == ymd(RunDateOxy))

```

Read in Run Specific O2Data
Make this more general as we accumulate more files.
```{r read data}
#temporary hack to cope with run date; replace with GREP? or map?
O2Data <- readRDS(file = file.path(DataInO2, paste("FluorO2_",RunDateOxy, "_O2Data.Rds", sep = "")))

```


Remove missing rows, reconcile time formats
```{r remove missing rows}
O2Data <- O2Data %>%
  filter(!is.na(LR_s)) %>%
  filter(TempCont == Cuvette) %>%
  filter(CultureID == StrainID) %>%
  mutate(ObsDate = ymd(RunDate),
         ObsTime = as.period(AbsTime),
         Ex_WL = as.factor(Ex_WL))

```

```{r prelimplot}
O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  #geom_point(aes(x = FRRfData$LR_s, y = FRRfData$JVPSII_aLHIIminmax)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  xlim(0, 1000) +
  theme_bw()

FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = ETRCtauav, colour = Ex_WL)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = ETRqpOxbo, colour = Ex_WL)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = ETRGorbo, colour = Ex_WL)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = JVPSII_ETRtauav_FoSig, colour = Ex_WL)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = JVPSII_ETRqpOxbo_FoSig, colour = Ex_WL)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = JVPSII_ETRtauav_aLHII_Sig, colour = Ex_WL)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = Ex_WL)) +
  #geom_point(aes(x = O2Data$LR_s, y = O2Data$O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()
```

## Simple left_join, some times line up
# Many blank rows after left join b/c most O2 rows do not have explicit FRRf row.  Possible problem if ObsTime gets out of sync b/t Optode & FRRf data captures
```{r leftjoin}
O2SlopeData <- left_join(x = O2Data, y = FRRfDataLight, by = c("ObsDate", "ObsTime", "CultureID", "Ex_WL", "TempCont"), suffix = c("O2", "FRRf"), keep = FALSE) %>%
  select(-c("RFID_User_Data":"Dur.Wat", "SNR_raw", "FP1", "nm445":"IRCorr")) 


#%>%
  #filter(LR_sO2 < 1080)  #202112130850_MURIS_caloxy_MaBe3729_AL590_Ex590_noTC.txt had an error, where the same time showed up twice 08:57:50 because of an optode lag; left_join only copied respective FRRf dark phase, but not AL-phase --> double NULL instead of 40, 0; fixed by altering time in original file by some microseconds to 08:57:49 and 08:57:50


```

```{r O2FRRfprelimplot}
O2SlopeData %>%
  #filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = LR_sO2, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_sO2, y = ActPARCorr), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  #xlim(0, 1080) +
  theme_bw()

```

Interpolate ActPARCorr estimates across entire time axis
```{r interpolate FRRf estimates}
#http://publish.illinois.edu/spencer-guerrero/2014/12/11/2-dealing-with-missing-data-in-r-omit-approx-or-spline-part-1/
#https://dplyr.tidyverse.org/dev/articles/colwise.html
#Interpolation causes problems with final rows that repeat last value.

interpolate <- function(x){zoo::na.locf(x, na.rm = FALSE, fromLast = TRUE, type = "l", maxgap = Inf)}

O2SlopeData <- O2SlopeData %>%
  mutate(ActPARCorrinter = interpolate(ActPARCorr),
         #Dark1sinter = interpolate(Dark1s), 
         LR_sFRRfinter = interpolate(LR_sFRRf), .after = Temp_C)
         
         #ActPARCorr_photonsm2sinter = interpolate(ActPARCorr_photonsm2s),
         #JVPSIIinter = interpolate(JVPSII_aLHIIminmax)

# test <- O2SlopeData %>%
#   filter(CultureID == "MaBe3433",
#          #LR_sO2 < 450,
#         Ex_WL == "590")
# 
# test %>%
#    #filter(Dark1sinter == 0) %>%
#    ggplot() +
#   geom_point(aes(x = LR_sO2, y = O2_umolL, colour = Ex_WL)) +
#  geom_point(aes(x = LR_sO2, y = ActPARCorrinter, colour = "black")) +
#     geom_point(aes(x = LR_sO2, y = Dark1sinter), colour = "red") +
#   scale_colour_manual(values = Colours_nm) +
#   facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
#   theme_bw()
```

Check whether ActPARCorrinter worked properly

```{r O2FRRfprelimplot2}
O2SlopeData %>%
  ggplot() +
  geom_point(aes(x = LR_sO2, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_sO2, y = ActPARCorrinter), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

#filter CultureID with negative O2slope throughout and with aberrant ActPARCorrinter
#recheck with Max about FRRf file processing to recuperate ActPARCorrinter
O2SlopeData %>%
  #filter(CultureID != "MaBe3432") %>%
  #filter(CultureID != "MaBe3431") %>%
  #filter(CultureID != "MaBe3433" | Ex_WL != "590") %>%
  #filter(CultureID %in% c("MaBe3433", "MaBe3436")) %>%
  ggplot() +
  geom_point(aes(x = LR_sO2, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_sO2, y = ActPARCorrinter), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

```

Estimate O2 slopes over LR PAR step ranges
Be careful with nesting!  Multiple steps at single ActPARCorrinter
Filter out first 50 s of each ActPARCorrinter set to skip 'induction' phase.
Filter out last 5 s to avoid Dark1s = 1 rows
```{r O2slopes}
induction_s = 50
end_s = 175

# GPP_model <- function(data) {
#   (((O2_umolLs - min(O2_umolLs)) * 6.022e17), data = data)
# }

O2Slopes <- O2SlopeData %>%
  #nest(O2data = -c(Date, CultureID, Ex_WL, filenameO2, ActPARCorrinter, LR_sFRRfinter)) %>% 
    nest(O2data = -c(Date, ActPARCorrinter,LR_sFRRfinter, filenameO2,CultureID, FileTime, CultureID, FileTime, CultureID, AL_WL, Ex_WL, TempCont, ObsDate)) %>%
  filter(!is.na(ActPARCorrinter)) %>%
  #nest(O2data = c(Date, AbsTime, LR_sO2, O2_umolL, Temp_C, ActPARCorrinter, filenameO2)) %>%
  mutate(O2lm = map(O2data,  possibly(~ lm(O2_umolL[induction_s:end_s] ~ as.numeric(AbsTime[induction_s:end_s]), data = .x), otherwise = NULL)),
         O2lm_tidy = map(O2lm, possibly(tidy, otherwise = NULL))) %>%
  select(-c(O2data, O2lm)) %>%
  unnest(cols = O2lm_tidy) %>%
  filter(term  != "(Intercept)") %>%
  select(-term) %>%
  rename(O2_umolLs = estimate) %>%
  group_by(Date, filenameO2, CultureID, Ex_WL) %>% #careful with group_by; this only works with a single replication of each LR with 5 steps per LR starting and ending with 0; redo to average all O2_umolLs at PAR = 0
  #mutate(O2evln_O2ls_OLD = (O2_umolLs - min(O2_umolLs)) * 6.022e17) %>%
  mutate(O2evln_O2ls = ((O2_umolLs - mean(O2_umolLs[1], O2_umolLs[5]))* photons_umol)) %>%
  # nest() %>%
  # mutate(O2evln_O2ls = map(.x = data, .f = ~GPP_model)) #%>%
  # mutate(O2evln_O2ls_ALT = map(.x = data, .f = ~((.x$O2_umolLs - mean(.x$O2_umolLs[1], .x$O2_umolLs[5]))))) %>%
  ungroup()

#Decide how to handle subtraction of dark O2 slopes to estimate gross O2 evln
#mutate(O2evln_O2ls_ALT = (O2_umolLs - mean(O2_umolLs[1], O2_umolLs[5]))) %>%
 #- (mean(O2_umolLs[1],O2_umolLs[5])))*6.022e17
```

```{r O2slopeplots}

O2Slopes %>%
  ggplot() +
  geom_line(aes(x = ActPARCorrinter, y = O2_umolLs, colour = Ex_WL)) +
    scale_colour_manual(values = Colours_nm) +
    facet_grid(cols = vars(CultureID), rows = vars(Ex_WL)) +
    theme_bw()

O2Slopes %>%
  ggplot() +
  geom_line(aes(x = ActPARCorrinter, y = O2evln_O2ls, colour = Ex_WL)) +
  #geom_line(aes(x = ActPARCorrinter, y = O2evln_O2ls_OLD, colour = "black")) +
    scale_colour_manual(values = Colours_nm) +
    facet_grid(cols = vars(CultureID), rows = vars(Ex_WL)) +
    theme_bw()
```

Merge O2Slopes Data with FRRf Data and Catalog

```{r}
O2FRRfMeta <- left_join(x = FRRfData, y = O2Slopes, by = c(c("ObsDate" = "Date"),  "CultureID", "Ex_WL", "ActPARCorr" = "ActPARCorrinter"), suffix = c("FRRf", "O2"), keep = FALSE) %>%
   left_join(x = ., y = MetaData, by = c("CultureID" = "id")) %>%
  filter(O2evln_O2ls > 0) %>%
  select(-c("tissue_treated_plate", "culture_inocul_L", "media_inocul_L", "target_media_id", "inoc_media_id", "nutrient_status", "imipenem_ug_mL", "cefoxitin_ug_mL", "meropenem_ug_mL", "ampicillin_ug_mL")) %>%
  select(-c("RFID_User_Data": "Dur.Wat"))

#%>%
  #select((-c("Alp4QA", "Tau4QA"))) %>% #only if present
  #mutate(TauQx = as.numeric(TauQx),
        # Cx = as.numeric(Cx))
```


# Cross plots of O2 evolution and FRRf electron transport estimators
```{r O2FRRfcrossplots}
O2FRRfMeta %>%
  filter(JVPSII_aLHIIOxbomax > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIOxbomax, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  theme_bw()


O2FRRfMeta %>%
  filter(ETRCtauav > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = ETRCtauav, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  theme_bw()

O2FRRfMeta %>%
  filter(ETRqpOxbo > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = ETRqpOxbo, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2ls, y = ETRqpOxbo, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(ETRGorbo > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = ETRGorbo, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2ls, y = ETRGorbo, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(JVPSII_ETRtauav_FoSig > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRtauav_FoSig, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRtauav_FoSig, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(JVPSII_ETRqpOxbo_FoSig > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo_FoSig, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo_FoSig, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(JVPSII_ETRtauav_aLHII_Sig > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRtauav_aLHII_Sig, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRtauav_aLHII_Sig, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(JVPSII_ETRqpOxbo_aLHII_Sig > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

```

For e- PSII-1 s-1 estimators like ETRqpOxbo, a plot vs. O2 evln_O2ls should give a linear regression.
[PSII] = (O2 evln_O2ls * 4)/(e- PSII-1 s-1)

Graphical Test for stability of [PSII] estimates.
```{r PSIIstabilitytestplot}
O2FRRfMeta %>%
  filter(ETRqpOxbo > 0) %>%
  ggplot() +
  geom_point(aes(y  = (O2_umolLs * 4)/ETRqpOxbo, x = ActPARCorr, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()

O2FRRfMeta %>%
  filter(ETRqpOxbo > 0) %>%
  ggplot() +
  geom_point(aes(y  = (O2evln_O2ls * 4)/ETRqpOxbo, x = ActPARCorr, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()


O2FRRfMeta %>%
  filter(ETRCtauav > 0) %>%
  ggplot() +
  geom_point(aes(y  = (O2evln_O2ls * 4)/ETRCtauav, x = ActPARCorr, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()

O2FRRfMeta %>%
  filter(ETRGorbo > 0) %>%
  ggplot() +
  geom_point(aes(y  = (O2evln_O2ls * 4)/ETRGorbo, x = ActPARCorr, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()


```

Estimates of [PSII] should be stable vs. ActPARCorr because [PSII] does not change appreciably during duration of light response measure.
If estimate of [PSII] change vs. ActPARCorr it indicates departures from assumptions in underlying data or estimators.

Filter O2-evolution values that are lower under higher light, caused by photoinhibion/alternative O2-pathways?
This may exclude reasonable values if low light values are exaggerated.
```{r InhibitionFilter}
O2FRRfMeta590 <- O2FRRfMeta %>%
  filter(Ex_WL == 590) %>%
  #filter(O2_umolLs < 0.05) %>% # for MaBe3729 20211210, TC
  filter(O2evln_O2ls > lag(O2evln_O2ls) & ActPARCorr > lag(ActPARCorr)) #%>%
  #filter(O2evln_O2ls > lead(O2evln_O2ls)) # for MaBe3726 20211210, noTC

O2FRRfMeta445 <- O2FRRfMeta %>%
  filter(Ex_WL == 445) %>%
  #filter(LR_sFRRfinter != 733) %>% #MaBe3727 20211210, TC
  #filter(LR_sFRRfinter != 732) %>% #for MaBe3726 20211210, noTC
  filter(O2evln_O2ls > lag(O2evln_O2ls) & ActPARCorr > lag(ActPARCorr))

O2FRRfMetaFilter <- rbind(O2FRRfMeta445, O2FRRfMeta590)

```


```{r InhibitionFilteredPSIIstabilitytestplot}
O2FRRfMetaFilter %>%
  filter(ETRqpOxbo > 0) %>%
  ggplot() +
  geom_point(aes(y  = (O2_umolLs * 4)/ETRqpOxbo, x = ActPARCorr, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()

O2FRRfMetaFilter %>%
  filter(ETRqpOxbo > 0) %>%
  ggplot() +
  geom_point(aes(y  = (O2evln_O2ls * 4)/ETRqpOxbo, x = ActPARCorr, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()

O2FRRfMetaFilter %>%
  filter(ETRCtauav > 0) %>%
  ggplot() +
  geom_point(aes(y  = (O2evln_O2ls * 4)/ETRCtauav, x = ActPARCorr, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()

O2FRRfMetaFilter %>%
  filter(ETRGorbo > 0) %>%
  ggplot() +
  geom_point(aes(y  = (O2evln_O2ls * 4)/ETRGorbo, x = ActPARCorr, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()

```


# Fit regressions of FRRf estimators vs. O2evln
```{r FRRFO2regressions}
#include representative 'augment' for test plots

O2FRRfMetaNest <-  O2FRRfMetaFilter %>%
  nest(data = -c(Ex_WL)) %>%
  mutate(
  JVPSII_aLHIIOxbomax_O2 = map(data, possibly(~lm(JVPSII_aLHIIOxbomax ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_aLHIIOxbomax_O2_tidied =  map(JVPSII_aLHIIOxbomax_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_aLHIIOxbomax_O2_param = map(JVPSII_aLHIIOxbomax_O2, possibly(glance, otherwise = NULL)),
  ETRCtauav_O2 = map(data, possibly(~lm(ETRCtauav ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  ETRCtauav_O2_tidied =  map(ETRCtauav_O2, possibly(tidy, otherwise = NULL)),
  ETRCtauav_O2_predict =  map(ETRCtauav_O2, possibly(augment, otherwise = NULL)),
  ETRCtauav_O2_param = map(ETRCtauav_O2, possibly(glance, otherwise = NULL)),
  ETRqpOxbo_O2 = map(data, possibly(~lm(ETRqpOxbo ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  ETRqpOxbo_O2_tidied =  map(ETRqpOxbo_O2, possibly(tidy, otherwise = NULL)),
  ETRqpOxbo_O2_param = map(ETRqpOxbo_O2, possibly(glance, otherwise = NULL)),
  ETRGorbo_O2 = map(data, possibly(~lm(ETRGorbo ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  ETRGorbo_O2_tidied =  map(ETRGorbo_O2, possibly(tidy, otherwise = NULL)),
  ETRGorbo_O2_param = map(ETRGorbo_O2, possibly(glance, otherwise = NULL)),
  JVPSII_ETRtauav_FoSig_O2 = map(data, possibly(~lm(JVPSII_ETRtauav_FoSig ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_ETRtauav_FoSig_O2_tidied =  map(JVPSII_ETRtauav_FoSig_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_ETRtauav_FoSig_O2_param = map(JVPSII_ETRtauav_FoSig_O2, possibly(glance, otherwise = NULL)),
   JVPSII_ETRqpOxbo_FoSig_O2 = map(data, possibly(~lm(JVPSII_ETRqpOxbo_FoSig ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_ETRqpOxbo_FoSig_O2_tidied =  map(JVPSII_ETRqpOxbo_FoSig_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_ETRqpOxbo_FoSig_O2_param = map(JVPSII_ETRqpOxbo_FoSig_O2, possibly(glance, otherwise = NULL)),
  JVPSII_ETRtauav_aLHII_Sig_O2 = map(data, possibly(~lm(JVPSII_ETRtauav_aLHII_Sig ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_ETRtauav_aLHII_Sig_O2_tidied =  map(JVPSII_ETRtauav_aLHII_Sig_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_ETRtauav_aLHII_Sig_O2_param = map(JVPSII_ETRtauav_aLHII_Sig_O2, possibly(glance, otherwise = NULL)),
  JVPSII_ETRqpOxbo_aLHII_Sig_O2 = map(data, possibly(~lm(JVPSII_ETRqpOxbo_aLHII_Sig ~ O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_ETRqpOxbo_aLHII_Sig_O2_tidied =  map(JVPSII_ETRqpOxbo_aLHII_Sig_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_ETRqpOxbo_aLHII_Sig_O2_param = map(JVPSII_ETRqpOxbo_aLHII_Sig_O2, possibly(glance, otherwise = NULL))
  )



O2FRRfMetaNest %>%
  unnest(ETRCtauav_O2_predict) %>%
  ggplot() +
  geom_line(aes(x = O2evln_O2ls, y = .fitted), colour = "black", linetype = "dashed") +
 #geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
 #geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
  geom_point(aes(x = O2evln_O2ls, y = ETRCtauav),colour = "darkgreen") +
  geom_point(aes(x = O2evln_O2ls, y = .resid), colour = "darkred", size = 0.1) +
  geom_hline(yintercept = 0,linetype = "dashed") +
  facet_grid(cols = vars(Ex_WL)) +
  theme_bw()
# 
# # O2FRRfMetaNest %>%
# #   unnest(JVPSII_O2_predict_alt) %>%
# #   ggplot() +
# #   geom_line(aes(x = O2evln_O2ls_ALT, y = .fitted), colour = "black", linetype = "dashed") +
# #  # geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
# #  #   geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
# #   geom_point(aes(x = O2evln_O2ls_ALT, y = JVPSII_aLHIIminmax),colour = "darkgreen") +
# #   geom_point(aes(x = O2evln_O2ls_ALT, y = .resid), colour = "darkred", size = 0.1) +
# #   geom_hline(yintercept = 0,linetype = "dashed") +
# #   facet_grid(cols = vars(Ex_WL)) +
# #   theme_bw()
# 
# O2FRRfMetaNest %>%
#   unnest(JVPSII_O2_tidied)#, JVPSII_O2_tidied_alt) 
# 
# O2FRRfMetaNest %>%
#   unnest(JVPSII_ETRqpOxbo_O2_predict) %>%
#   ggplot() +
#   geom_line(aes(x = O2evln_O2ls, y = .fitted), colour = "black", linetype = "dashed") +
#  # geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
#  #   geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
#   geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo),colour = "darkgreen") +
#   geom_point(aes(x = O2evln_O2ls, y = .resid), colour = "darkred", size = 0.1) +
#   geom_hline(yintercept = 0,linetype = "dashed") +
#   facet_grid(cols = vars(Ex_WL)) +
#   theme_bw()

# O2FRRfMetaNest %>%
#   unnest(JVPSII_ETRqpOxbo_O2_predict_alt) %>%
#   ggplot() +
#   geom_line(aes(x = O2evln_O2ls_ALT, y = .fitted), colour = "black", linetype = "dashed") +
#  # geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
#  #   geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
#   geom_point(aes(x = O2evln_O2ls_ALT, y = JVPSII_ETRqpOxbo),colour = "darkgreen") +
#   geom_point(aes(x = O2evln_O2ls_ALT, y = .resid), colour = "darkred", size = 0.1) +
#   geom_hline(yintercept = 0,linetype = "dashed") +
#   facet_grid(cols = vars(Ex_WL)) +
#   theme_bw()


```


```{r save O2FRRfMeta}
saveRDS(O2FRRfMetaFilter, file.path(DataOut, paste(Project, RunDateOxy, Cuvette, StrainID, "O2FRRfMeta.Rds", sep = "_"), fsep = .Platform$file.sep))

saveRDS(O2FRRfMetaNest, file.path(DataOut, paste(Project, RunDateOxy, Cuvette, StrainID, "O2FRRfMetaNest.Rds", sep = "_"), fsep = .Platform$file.sep))

```


