---
title: "O2ImportTidy"
author:

- Douglas A. Campbell
- Maximilian Berthold
- Laurel Genge
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

##Introduction
We use an optode to measure [O2] µmol l-1 in suspensions of phytoplankton.
Changes in [O2] reflect (hopefully) oxygen evolution or oxygen consumption by the cell suspension.

## Materials and Methods

This .Rmd Rworkbook imports data in simple .txt .tsv form exported from FireSting optodes based upon project specific values for variables set by the user.

It tidies and organizes the data.

To-Do list:

variable name is in two rows, need to find a way to make variable name in two rows into one row.
Need to match the tube number from file name with Ch1O2 etc... 
Need to match each run with date from catalog
create preiminary graphs

#Priority List
-single data file import for O2
-multi-file batch data import (may not be fully feasible given we need match multiple files together in some cases)
-O2 preliminary plots
-merge O2 plots as over-lays of growth plots (time axis may be tricky but I think I know how)

First Try Import Dialog Under 'Environment' to import a single file into a dataframe.

File delimiter is '.tsv' b/c the instrument software is from Europe.

Appears to be 11 rows of 'Header' Information to skip.
```{r paste code from Import dialog}

library(readr)
X202204061316_PICO_caloxy_SySl1156_445_LL <- read_delim("Optode/SySlCCACaloxy/202204061316_PICO_caloxy_SySl1156_445_LL.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(X202204061316_PICO_caloxy_SySl1156_445_LL)

#raw paste fails b/c need to change file path

X202204061316_PICO_caloxy_SySl1156_445_LL <- read_delim("../Optode/SySlCCACaloxy/202204061316_PICO_caloxy_SySl1156_445_LL.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(X202204061316_PICO_caloxy_SySl1156_445_LL)
```

Many issues with raw imported file:
-all 'columns' converted to 'character' type because they contain more than one type of data

-'Header' or 'Meta' data rows at top of file incorrectly included as 'data'
-many 'non-syntatical' variable names, and variable values that may cause problems later.
  Variable names need to start with a letter, and must only include letters, numeral or '_'.
  Variable values should only include letters, or numerals, or letters + numerals + '_'
  
-'Variable Names' are present on multiple rows
-Separate variables are concatenated into single columns b/c of issues with 'Variable Names'

So, try again, setting 'skip' value to jump over 
```{r import dialog paste, retry}
library(readr)
X202204061316_PICO_caloxy_SySl1156_445_LL <- read_delim("../Optode/SySlCCACaloxy/202204061316_PICO_caloxy_SySl1156_445_LL.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE, skip = 13)
View(X202204061316_PICO_caloxy_SySl1156_445_LL)

colnames(X202204061316_PICO_caloxy_SySl1156_445_LL)
```

Now we have:
-multiple columns in which all values are 'NA'
-multiple columns in which all values are '---'
-multiple columns with non-syntatical names

There is no clear means to solve these problems through the 'Import' dialog.

An Approach:
-find code to identify and remove columns which are only 'NA' or only '---'
to simplify our work
  That may cause problems if different files for later import have different 'empty' columns
-re-name remaining columns with syntatical variable names
  That may cause problems if different files for later import have different column names or orders

```{r filter 'is.na'}
#switch to more convenient name for dataframe and remove columns which are all 'NA'
OptodeTest <- X202204061316_PICO_caloxy_SySl1156_445_LL %>%
  select(
    where(
      ~!all(is.na(.x)) #remove columns of all na
    )
  )
```

```{r filter columns with only ---}
#https://stackoverflow.com/questions/41815039/remove-columns-that-contain-a-specific-word
#remove columns which only contain value '---'
OptodeTest2 <- OptodeTest %>%
  select(
    where(
      ~!all(str_detect(.x, pattern = "---")) #remove columns containing only all "---"
    )
  )
```

  
# Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "FluorO2"

Run <- "SySlCCACaloxy"


FileID <- "caloxy"
DataIn <- file.path("..", "Optode", Run)
DataOut <- file.path("..","ImportData", "Optode")
#MetaCatalog <- file.path("..","PicoCatalog.csv")

FileEncode <- "UTF-8" 
Delimiter <- "\t"

#fixed HeaderRows is brittle; better to figure out how to read all data starting at line that contains 'key'
HeaderRows <- 19
Comment <- "#"

#Set URL for MetaData
MetaDataURL <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"
```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
#library(stringr)
library(broom)
#library(knitr)
#library(zoo)
#library(tidyquant)
library(googlesheets4)
library(googledrive)
#library(dplyr)
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

This chunk reads in the MetaData catalog from googlesheets 
```{r load Catalog, now as a google sheet}
 gs4_deauth()
# #deauthorizes access to googlesheet
# 
 MetaCatalog <- read_sheet(MetaDataURL) %>%
# # sheet is read in by sheet ID, obtained from the URL of the sheet.
# # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
# # ggplot/dplyr doesn't like working with a dataframe of lists.
# # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# # To fix this, first drop all rows missing WL, then unlist.
# # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
# 
 drop_na(WL) %>%
   mutate(WL = unlist(WL))
 
 as.data.frame(MetaCatalog)
```

listing the names of the oxygen data, classified as DataIn. DataIn = O2Data 
```{r O2Data files}

#recursive = TRUE sets function to go down directory path
O2DataFiles <- list.files(path = DataIn, pattern = FileID, full.names = TRUE, recursive = TRUE)

#check file names
O2DataFiles

O2DataFiles<-  grep('txt', O2DataFiles, value = TRUE, invert = FALSE)

#only retain .txt files
O2DataFiles
```

Creates function using data.table::fread to skip the beginning comments and starts reading file after key word "Data". Second function read_tsv_plus adding file name and skips header rows to start reading file after. Data read.delim_plus or read_delim_plus adds filename and cdate, message=FALSE, warning=FALSE
```{r creating functions to read in data}

#function adds filename and cdate and controls when R starts to read the file, skips header rows
#fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = "Date [A Ch.1 Main]" ) %>% mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))}


#function allows you to read in oxygen data files (Reads in Run14 files)
read_tsv_plus <- function(Flnm, HeaderRows){read_tsv(Flnm,  col_names = TRUE,  comment = Comment) %>%
    mutate(filename = Flnm)}

#generates a read function using tidyverse::read_delim
 #read.delim_plus <- function(flnm, FileEncode, Delimiter, HeaderRows){read.delim(flnm, fileEncoding = FileEncode, sep = Delimiter,  skip = HeaderRows, row.names = NULL) %>%
     #mutate(filename = flnm, cdatetime = ymd_hms(file.info(flnm)$ctime))}

#Adds filename and cdate
#read_delim_plus <- function(Flnm, Delimiter, HeaderRows, Comment){read_delim(file = Flnm, delim = Delimiter, comment = Comment, skip = HeaderRows) %>%
     #mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))}
 
```


Reads in O2Data, and skips the "notes" at the beginning of the data and begins to read after HeaderRows. Renames columns so there are no duplicates (.name_repair)
```{r read optode data}

#brittle to use column numbers; needs to be changed if using multiple channels
O2Data <- O2DataFiles %>% 
  map_df(~read_tsv_plus(Flnm = ., HeaderRows = 19)) %>%
  select(c(1:4, 12, "Time [Comment]","Comment","filename")) %>%
  rename(Date = `Date [A Ch.1 Main]`, 
         AbsTime = `Time [A Ch.1 Main]`,
         LR_s = `dt (s) [A Ch.1 Main]`,
         O2_umolL = `Oxygen (\xb5mol/L) [A Ch.1 Main]`, 
         Temp_C = `Sample Temp. (\xb0C) [A Ch.1 CompT]`,
         CommentTime = `Time [Comment]`) %>%
  mutate(CommentTime = hms::new_hms(as.numeric(CommentTime) + (3600 * 12)))

O2Data <- O2Data %>%
  mutate(filename = str_remove(string = filename, pattern = ".txt")) %>%
  mutate(filename = str_remove(string = filename, pattern = "../RawData/Optode/")) %>%  
  separate(filename, into = c("RunDate", "FileDate","FileTime", "Project", "FileID", "CultureID", "Ex_WL"), sep = "([\\/\\_\\_\\_\\_\\_])", remove = FALSE) %>%
  mutate(FileTime = parse_date_time(as.character(FileTime), "hms")) %>%
  separate(FileTime, into = c("FileYear", "FileTime"), sep = "([ ])", remove = TRUE) %>%
  select(-c(FileYear))

O2Data[1:5,]
```

```{r prelimplot}
O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()
```


```{r save SolFitsTrim data}
saveRDS(O2Data, file.path(DataOut, paste(Project, RunDate, "O2Data.Rds", sep = "_"), fsep = .Platform$file.sep))
```



