---
title: "O2ImportTidy"
author:

- Douglas A. Campbell
- Maximilian Berthold
- Laurel Genge
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
We use an optode to measure [O2] µmol l-1 in suspensions of phytoplankton.
Changes in [O2] reflect (hopefully) oxygen evolution or oxygen consumption by the cell suspension.

# Materials and Methods

This .Rmd Rworkbook imports data in simple .txt .tsv form exported from FireSting optodes based upon project specific values for variables set by the user.

It tidies and organizes the data.

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
```

## To-Do list:

variable name is in two rows, need to find a way to make variable name in two rows into one row.
Need to match the tube number from file name with Ch1O2 etc... 
Need to match each run with date from catalog
create preiminary graphs

## Priority List
-single data file import for O2
-multi-file batch data import (may not be fully feasible given we need match multiple files together in some cases)
-O2 preliminary plots
-merge O2 plots as over-lays of growth plots (time axis may be tricky but I think I know how)

## First Try Import Dialog Under 'Environment' to import a single file into a dataframe.

File delimiter is '.tsv' b/c the instrument software is from Europe.

```{r paste code from Import dialog}

library(readr)
X202204061316_PICO_caloxy_SySl1156_445_LL <- read_delim("Optode/SySlCCACaloxy/202204061316_PICO_caloxy_SySl1156_445_LL.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(X202204061316_PICO_caloxy_SySl1156_445_LL)

#raw paste fails b/c need to change file path

X202204061316_PICO_caloxy_SySl1156_445_LL <- read_delim("../Optode/SySlCCACaloxy/202204061316_PICO_caloxy_SySl1156_445_LL.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(X202204061316_PICO_caloxy_SySl1156_445_LL)
```

## Issues with raw imported file:

-all 'columns' converted to 'character' type because they contain more than one type of data

-~13 rows of 'Header' or 'Meta' data rows at top of file are incorrectly included as 'data'

-Many variable names are 'non-syntatical' for R.
  Variable names for R need to start with a letter, and must only include letters, numeral or '_'.
  
-Some variable values  may cause problems later.
  Variable values for R should only include letters, or numerals, or letters + numerals + '_'
  In a DataFrame all values in a column must be of the same 'class'; all numeric; all character; all logical; all factor
  In a DataFrame all columns must be of the same length.
  (Technical detour:
A DataFrame is a 'list' of named 'atomic vectors', with each vector the same length.  The names of the vectors are the variable names; the elements of the vectors are the aligned rows.)
  
-'Variable Names' are present on multiple rows
-Separate variables are concatenated into single columns b/c of issues with 'Variable Names'

So, try again, setting 'skip' value for number of rows to jump over.
Setting a fixed number of rows to jump over is 'brittle', and will fail if a given file had a slightly different 'header' structure.

```{r import dialog paste, retry}
#library(readr)
X202204061316_PICO_caloxy_SySl1156_445_LL <- read_delim("../Optode/SySlCCACaloxy/202204061316_PICO_caloxy_SySl1156_445_LL.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE, skip = 13)
View(X202204061316_PICO_caloxy_SySl1156_445_LL)

colnames(X202204061316_PICO_caloxy_SySl1156_445_LL)

```

Now we have:
-multiple columns in which all values are 'NA'
-multiple columns in which all values are '---'
-multiple columns with non-syntactical names

There is no clear means to solve these problems interactively through the 'Import' dialog.

An Approach:
-Find code to identify and remove columns which contain only 'NA' or only '---'
to simplify our work
  That may cause problems if different files for later import have different 'empty' columns
  
-Re-name remaining columns with syntactical variable names
  That may cause problems if different files for later import have different column names or orders

```{r remove columns containing only 'NA'}
#Remove columns which are all 'NA'
OptodeTest <- X202204061316_PICO_caloxy_SySl1156_445_LL %>%
  select(
    where(
      ~!all(is.na(.x)) #remove columns of all na
    )
  )
```

```{r remove columns containing only ---}
#https://stackoverflow.com/questions/41815039/remove-columns-that-contain-a-specific-word
#remove columns which only contain value '---'
OptodeTest2 <- OptodeTest %>%
  select(
    where(
      ~!all(str_detect(.x, pattern = "---")) #remove columns containing only all "---"
    )
  )

colnames(OptodeTest2)
```

```{r rename non-syntactical variable names}

#CampbellCase_unit variable naming convention followed; following a convention makes variable naming easier and more consistent.

#Remove superfluous columns from working dataframe; be careful!
#Renaming involves knowledge of what data is actually present to give sensible names
#Enclose problematic character strings in `` so R does not attempt to interpret strings as code etc.

OptodeTest3 <- OptodeTest2 %>%
  select(-c(`(mbar)`, `(%)`,`('C)...15`,`Ch 1...18`,`Ch1...22`,`Ch1...26`)) %>%
  rename(Time_hms = `Time (HH:MM:SS)`,
         ETime_s = `Time (s)`,
         O2_umolL = `Ch1...5`,
         Temp_C = `Ch 1...9`)

head(OptodeTest3)
```

Reality Therapy Plot
```{r reality therapy plot}
OptodeTest3 %>%
  ggplot() +
  geom_point(aes(x = ETime_s, y = O2_umolL)) +
  theme_bw()

OptodeTest3 %>%
  ggplot() +
  geom_point(aes(x = ETime_s, y = Temp_C)) +
  theme_bw()
```

We have code to import and tidy a single file from the PyroOxyLog Oxygen Optode monitoring system.

We could save the tidied DataFrame as a .csv for use elsewhere, or as an .Rds file for re-use within R.

```{r save OptodeTest data}
write_csv(x = OptodeTest3, file = file.path("OptodeTest3.Rds", fsep = .Platform$file.sep))

#note slightly different syntax for saveRDS
saveRDS(OptodeTest3, file = file.path("OptodeTest3.Rds", fsep = .Platform$file.sep))
```

But, we have thousands of such files with ~~identical structures~~, containing data from different runs.

Could we implement a bulk import and assembly of the data from multiple files into a common dataframe?

  
# Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables for bulk import}
#"..", takes up a level in the directory path
Project <- "FluorO2"

Run <- "SySlCCACaloxy"

FileID <- "caloxy"
DataIn <- file.path("..", "Optode", Run)
DataOut <- file.path("..","ImportData", "Optode")
#MetaCatalog <- file.path("..","PicoCatalog.csv")

FileEncode <- "UTF-8" 
Delimiter <- "\t"

#fixed 'Skip' is brittle and will fail if number of header rows varies across files
HeaderRows = 13
Comment <- "#"

#Set URL for MetaData
MetaDataURL <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"
```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(googlesheets4)
library(googledrive)

#library(knitr)
#library(zoo)
#library(tidyquant)
```

```{r set colours}
#Setting a vector of wavelength values, then using it to 'name' a vector of R colour values will allow us to assign colours to wavelengths later
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

This chunk reads in the MetaData catalog from googlesheets
MetaData for each culture was entered manually; including a serial SampleID (ex. SySl1001) for each sample, which is included in names of data files derived from that sample.
```{r load Catalog, now as a google sheet}
 gs4_deauth()
# #deauthorizes access to googlesheet
# 
 MetaCatalog <- read_sheet(MetaDataURL) %>%
# # sheet is read in by sheet ID, obtained from the URL of the sheet.
# # read_sheet sets the type of columns it can't parse to a list.
# # ggplot/dplyr does not work well with a dataframe of lists.
# # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# # To fix this, first drop all rows missing WL, then unlist.
# # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
# 
 drop_na(WL) %>%
   mutate(WL = unlist(WL))
 
 as.data.frame(MetaCatalog)
```

listing the names of the oxygen data, path stored in variable DataIn.
```{r O2Data files}

#recursive = TRUE sets function to go down directory path; recursive = FALSE will only read files at the level of the assigned directory, not in sub-folders
O2DataFiles <- list.files(path = DataIn, pattern = FileID, full.names = TRUE, recursive = FALSE)

#check file names
#O2DataFiles

O2DataFiles <-  grep('txt', O2DataFiles, value = TRUE, invert = FALSE)

#only retain .txt files
length(O2DataFiles)
O2DataFiles

```

We have a path to a folder that contains `r length(O2DataFiles)` saved in the .txt format we seek.
This data set is big enough to be worth a bulk import, but small enough to handle.

Create function read_tsv_plus adding file name and skips header rows to start reading file after string "Data" read.delim_plus or read_delim_plus adds filename and cdate, message=FALSE, warning=FALSE

Alternate function using data.table::fread skips the beginning comments and starts reading file after key word "Data".
```{r creating functions to read in data}
#a read function using tidyverse::read_delim that skips a fixed number of header rows, and adds columns to the dataframe containing the filename and the file creation date time.
read_delim_plus <- function(flnm, delimiter, headerrows, fileencode){read_delim(flnm, delim = delimiter,  col_names = TRUE,  comment = Comment, skip = headerrows, escape_double = FALSE,  locale = locale(encoding = fileencode), trim_ws = TRUE, ) %>%
    mutate(Filename = flnm,
           Cdatetime = ymd_hms(file.info(flnm)$ctime))
  }


#a read function using data.table::fread that skips header rows up to occurence of a character string, and adds columns to the dataframe containing filename and cdate.
#fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = "Date [A Ch.1 Main]" ) %>% mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))}


 
```


"../Optode/SySlCCACaloxy/202204061316_PICO_caloxy_SySl1156_445_LL.txt"


Reads in O2Data files one after another; skips the header "notes" at the beginning of the data and begins to read each file after HeaderRows. Renames columns so there are no duplicates (.name_repair).

There are multiple functions from baseR ('read.delim'), from Tidyverse ('read_delim') or from data.table ('fread') for reading in files; if one approach fails; try another.
Pipe read files directly to cleaning steps; could do cleaning transforms within 'map_df' as well
```{r read optode data}

O2Data <- O2DataFiles %>%
  map_df(~read_delim_plus(flnm = ., delimiter = Delimiter, headerrows = HeaderRows, fileencode = FileEncode)) %>%
  select(
    where(
      ~!all(is.na(.x)) #remove columns of all na
    )
  ) %>%
  select(
    where(
      ~!all(str_detect(.x, pattern = "---")) #remove columns containing only all "---"
    )
  ) %>%
  select(-c(`(mbar)`, `(%)`,`('C)...15`,`Ch 1...18`,`Ch1...22`,`Ch1...26`)) %>%
  rename(Time_hms = `Time (HH:MM:SS)`,
         LR_s = `Time (s)`,
         O2_umolL = `Ch1...5`,
         Temp_C = `Ch 1...9`)
  
head(O2Data)
```

#Generate columns from Filename
```{r generate columns from Filename}
"../Optode/SySlCCACaloxy/202205181355_PICO_caloxy_SySl1246_535_LL.txt"
"SySlCCACaloxy/202205181355_PICO_SySl1246_535_LL"

O2Data <- O2Data %>%
  mutate(Filename = str_remove(string = Filename, pattern = "../Optode/"),
         Filename = str_remove(string = Filename, pattern = ".txt"),
         Filename = str_remove(string = Filename, pattern = "caloxy_")) %>%
  separate(Filename, into = c("Run", "FileDateTime", "Project", "CultureID", "Ex_WL", "GrowthLight"), sep = "([\\/\\_\\.])", remove = FALSE) %>%
  mutate(FileDateTime = parse_date_time(as.character(FileDateTime), orders = "ymdHM")) %>%
  separate(FileDateTime, into = c("ObsDate", "ObsTime"), sep = "([ ])", remove = FALSE) %>%
  mutate(ObsDate = ymd(ObsDate),
         ObsTime = hms(ObsTime))

head(O2Data)

#for compatibility add TempCont column
O2Data <- O2Data %>%
  mutate(TempCont = "TC")

```
Fix column classes
```{r fix column classes}
O2Data <- type_convert(O2Data) %>%
  mutate(Ex_WL = as.factor(Ex_WL))

head(O2Data)
```


```{r prelimplot}
O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  coord_cartesian(xlim = c(0,1200)) +
  theme_bw()
```


```{r save SolFitsTrim data}
saveRDS(O2Data, file.path(DataOut, paste(Project, Run, "O2Data.Rds", sep = "_"), fsep = .Platform$file.sep))
```



